Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-08-19 manuscript/Chapter3-manuscript.Rmd
added figure 3 to MS. might delete later
update MS with correct figure 4

>>>>

blablabla figure 3

```{r out.width = "100%", fig.cap = "**Figure 3.** Title (A) Novice. (B) Advanced."}
knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure3.png"))
```

blablabla figure 4

```{r out.width = "100%", fig.cap = "**Figure 4.** Title (A) and (B) Novice. (C) and (D) Advanced."}
knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure4.png"))
```
